How to Avoid OOTA Without Really Trying

### 2024-10-06 paper/ootavacuous.tex
ootavacuous: Section 7.4 optimization non-recommendation
Suggested-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Although it is unexpected, we cannot say that this conclusion is
definitely wrong, because our intuitive notions of semantic
dependency are not clear in cases where multiple loads of the same
variable are present.
% Can we instead say that transforming the code might require that the
% witness also be transformed?

>>>>

Although it is unexpected, and while we don't recommend this sort of code
transformation, we cannot say that this conclusion is definitely wrong,
because our intuitive notions of semantic dependency are not clear in
cases where multiple loads of the same variable are present.
% Can we instead say that transforming the code might require that the
% witness also be transformed?
